---
title: "Pitch_project COVID 19 Shiny Dashboard"
author: "annasbest"
date: "11/13/2022"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE
)
options(knitr.table.format = "html") 
```

```{r, echo=FALSE}
library(COVID19)
```

# Description

This presentation is done for the Coursera course Developing Data Products. The final assignment was to create a Shiny app and a reproducible pitch because it is fun :-)

Access the shiny app [here](https://benthecoder.shinyapps.io/COVID-19_Dashboard/)

Access the github repo that hosts the files [here](https://github.com/benthecoder/JohnHopkinsDataScience/tree/main/9_DevelopingDataProducts/projects/COVID-19_Dashboard)

This will be going into how the shiny app was formed, and where the data comes from. 


# COVID-19 Data 

The data was provided with a package by the COVID-19 Data Hub, which you can access [here](https://covid19datahub.io/articles/api/r.html)

Look at the Documentation [here](https://covid19datahub.io/articles/doc/data.html) 

Download the data [here](https://covid19datahub.io/articles/data.html)

Citation

> Guidotti et al., (2020). COVID-19 Data Hub. Journal of Open Source Software, 5(51), 2376, https://doi.org/10.21105/joss.02376

# Define User Interface

The COVID19 R package provides an integration with COVID-19 Data Hub via the covid19() function.

```{r eval=FALSE}
# structure of the user interface
ui <- fluidPage(
    selectInput("country"...)
    selectInput("type"...)
    selectInput("level"...)
    dateRangeInput("date"...)
    plotlyOutput("covid19plot")
    
)
```


# Server Logic

Below shows the server.R code!

```{r eval=FALSE}
# Define server logic
server <- function(input, output) {
    output$covid19plot <- renderPlotly({
        if (!is.null(input$country)) {
            x <- covid19(
                    country = input$country,
                    level = input$level,
                    start = input$date[1],
                    end = input$date[2]
                )
            color <- paste0("administrative_area_level_", input$level)
            plot_ly(x = x[["date"]],
                    y = x[[input$type]],
                    color = x[[color]],
                    type = 'scatter',
                    mode = 'lines')
            
        }
    })
    
}
```
